### 2019-08-12 thesis.tex
last night!
* thesis.tex: Summary: last night, she said...

Inside the heliosphere, objectives of solar and space physics are
understanding the evolution and dynamics of the Sun,

\subsection{Solar and space physics research}
\label{sec:topics}

As described above, particles ejected by the Sun determine the overall
dynamics of the interplanetary medium until the termination shock boundary.
Beyond this limit, the solar wind still has a significant influence on
the nature of the local interstellar space for a long distance up to the
heliopause. As a well established scientific discipline, solar and space
physics work towards developing a better comprehension of the Sun and
the solar processes molding this vast and complex dynamic system called
heliosphere.

@@

\begin{figure}[h]
  \begin{center}
    \includegraphics[width=0.9\textwidth]{ESA_s_fleet_of_Solar_System_explorers_2019.jpg}
    \caption{ESA's past, present, and future science missions for studying the solar system.}
      {\footnotesize Credit:}
      \href{https://www.esa.int/spaceinimages/Images/2019/02/ESA_s_fleet_of_Solar_System_explorers}
      {\footnotesize ESA}{\footnotesize , accessed at 10/08/2019.}
    \label{esa}
  \end{center}
\end{figure}

\begin{figure}[h]
  \begin{center}
    \includegraphics[width=0.9\textwidth]{hso_fleet_chart_april_2019.pdf}
    \caption{NASA's present and future heliophysics system observatory. The number
      between parenthesis under the probe's name is the total number of spacecrafts
      that compose the mission.}
      {\footnotesize Credit:}
      \href{https://science.nasa.gov/heliophysics}
      {\footnotesize NASA}{\footnotesize , accessed at 10/08/2019.}
    \label{nasa}
  \end{center}
\end{figure}

>>>>

The extension of the influence that the plasma ejected from the Sun has, puts
in perspective the fundamental role played by plasma physics in the solar and
space physics research. %% talk about some key processes

Inside the heliosphere, the Sun, the space environment around Earth and the
interplanetary medium are extensively explored by space probes.
%% say something about it

Figures
\ref{nasa} and \ref{esa} illustrate the current space missions of NASA and the
European Space Agency (ESA), respectively. Describing the processes assessed by
each one of the illustrated probes it is out of the scope of this work\footnote{
  For a complete description, of the NASA missions is available at
\url{https://science.nasa.gov/missions-page?field_division_tid=5&field_phase_tid=All}.
For the ESA missions, go to \url{http://sci.esa.int/home/51459-missions/}.
  Both sites were accessed at 11/08/2019.}.
\begin{figure}[h]
  \begin{center}
    \includegraphics[width=0.9\textwidth]{hso_fleet_chart_april_2019.pdf}
    \caption{NASA's present and future heliophysics system observatory. The number
      between parenthesis under the probe's name is the total number of spacecrafts
      that compose the mission.}
      {\footnotesize Credit:}
      \href{https://science.nasa.gov/heliophysics}
      {\footnotesize NASA}{\footnotesize , accessed at 10/08/2019.}
    \label{nasa}
  \end{center}
\end{figure}
\begin{figure}[h]
  \begin{center}
    \includegraphics[width=0.9\textwidth]{ESA_s_fleet_of_Solar_System_explorers_2019.jpg}
    \caption{ESA's past, present, and future science missions for studying the solar system.}
      {\footnotesize Credit:}
      \href{https://www.esa.int/spaceinimages/Images/2019/02/ESA_s_fleet_of_Solar_System_explorers}
      {\footnotesize ESA}{\footnotesize , accessed at 10/08/2019.}
    \label{esa}
  \end{center}
\end{figure}
% As described above, ionized particles ejected by the Sun determine the
% overall dynamics of the interplanetary medium until the termination shock
% boundary. Beyond this limit, the solar wind still has a significant
% influence on the nature of the local interstellar space for a long distance
% up to the heliopause.
% As a well established scientific discipline, solar and space physics work
% towards developing a better comprehension of the Sun and
% the solar processes molding this vast and complex dynamic system called
% heliosphere.

@@
